---
title: "FARS Functions"
author: "Christopher Brown"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r "setup", include=FALSE}
require("knitr")
require("dplyr")
require("maps")
require("graphics")
opts_knit$set(root.dir = "C:/Users/cbrown/Desktop/R_Projects/Course3Assignment/R/")
opts_chunk$set(warning=F,message=F)
```

## Overview
The FARS Functions package provides several functions for importing
and analyzing data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS).

Briefly, the functions in the FARS functions package are:

* **fars_read(my_file)** - Reads data from a FARS data csv file and returns a data frame tbl object.

* **make_filename(year)** - Makes a filename from a given year

* **fars_read_years(list_of_years)** - Converts a vector of years to a list of filenames and reads data from those files

* **fars_summarize_years(list_of_years)** - Reads data from files and organizes data by year and month

* **fars_map_state(state,year)** - Read data from files and plots accidents in a given state and year on a map.

Typically, one wants to use **fars_read_years** to read data, **fars_summarize_years** to read and summarize data, and **fars_map_state** to read and visualize data.

## Examples of use
```{r echo=FALSE}
source("fars_functions.R")
```
Read in a few years worth of data.
```{r}
df <- fars_read_years(c(2013,2014,2015))
```
We can read and summarize data in one or more years:
```{r}
df <- fars_summarize_years(2013)
print(df)
```
We can also read and visualize data form a given state in a given year.
```{r}
fars_map_state(22,2013)
```
